---
title: "h Index Over Years"
author: "Jose V. Die"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `hIndex` pkg. gets graphical representation of the h Index over the years for a given author.

This R-package is motivated by the reading of [How does a scientist's h-index change over time?](https://jeffollerton.wordpress.com/2015/05/10/how-does-a-scientists-h-index-change-over-time/), 
by  **Jeff Ollertons**, Professor of Biodiversity in the Department of Environmental and Geographical Sciences at the University of Northampton. It is a great post and I highly recommend it.

By using `hIndex` you will be able to:  
  
  * observe how your h-index has changed over your career time
  * compare your h-index change with others scientists'change
  * estimate how long it takes on average to get 1 citation for your most highly accessed papers (from publication date to present). 
    
 <br>  
     
### Installation 
Install the pkg. in three simple steps:  
 
 **Step1**. You need to install the [devtools](https://github.com/hadley/devtools) package.

```{r eval=FALSE}
install.packages("devtools")
```

**Step2**. Load the devtools package.

```{r, eval=FALSE}
library(devtools)
```

**Step3**. Install the **hIndexOverYears** package. 

```{r, eval=FALSE}
install_github("jdieramon/hIndex")
```


### Usage
Load the package ...

```{r}
library(hIndexOverYears)
```

... and use it ! 

The function `clean` will read and clean the data from SCOPUS.
 
```{r}
dat <- clean("../CTOExport.csv")
```


Use the `h.plot` function on the tidy data to show the *h* Index evolution over years. If the starting year does not correspond with h=0, you can enter the h value as an argument:
```{r fig.align='center',fig.cap='My h index over the years', fig.width = 5 }
h.plot(dat, 2007, 2018, 0)
```

<br>  
  
  
You may also want to use the `get1cite` function to list your most highly cited papers (top10) and get a sense of **how long it takes each of them to get 1 citation**. 
The function shows by default your top10 cited papers, but you can give the number of papers as an argument. 

```{r}
get1cite(dat)
```

